A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2021-01-20 05_Post-hoc_analysis_Investigation.Rmd
correct object names

Let's estimate the age of the crop based on crop maturity observations, we will use the `PM_MB_dat` which include some observations of crop maturity.

```{r whatAreTheAges}
dat2 <- PM_MB_dat %>%
   mutate(
      flower = lubridate::ymd(flowering_date) - lubridate::ymd(planting_date),
      pod = lubridate::ymd(pod_fill_date) - lubridate::ymd(planting_date),
      late_pod = lubridate::ymd(mid_late_pod_fill) - lubridate::ymd(planting_date)
   ) %>%
   select(location, year, flower, pod, late_pod) %>%
   distinct() %>%
   arrange(desc(flower))

>>>>

Let's estimate the age of the crop based on crop maturity observations, we will use the `PM_MB_dat_full` which include some observations of crop maturity.

```{r whatAreTheAges}
dat2 <- PM_MB_dat_full %>%
   mutate(
      flower = lubridate::ymd(flowering_date) - lubridate::ymd(planting_date),
      pod = lubridate::ymd(pod_fill_date) - lubridate::ymd(planting_date),
      late_pod = lubridate::ymd(mid_late_pod_fill) - lubridate::ymd(planting_date)
   ) %>%
   select(location, year, flower, pod, late_pod) %>%
   distinct() %>%
   arrange(desc(flower))
